\documentclass{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{enumerate}
\pdfpageheight 11in
\pdfpagewidth 8.5in
\hoffset = -0.7 in
\voffset = -0.5 in
\textwidth = 7.9in
\textheight = 10 in
\usepackage{multicol}
\pagestyle{empty}
\renewcommand*\sfdefault{ugq}
\usepackage[T1]{fontenc}
\setlength{\parindent}{0pt}


\begin{document}

\begin{multicols}{2}

{\bfseries
	{\Huge Quentin } \\
	{\Huge Donnellan }
}
\columnbreak


{\raggedleft
	quentin@qdonnellan.com {\bf :EMAIL}\\
	817-993-9184 {\bf :PHONE}\\
	qdonnellan.com {\bf :WEBSITE}\\
	github.com/qdonnellan {\bf :GITHUB}\\
}


\end{multicols}
\textbf{\large gist:} \textit{\large a high school calculus teacher with engineering degree and two years self-taught Python web-development experience is actively pursuing full-time opportunities in software development }
\begin{center}
\rule{\textwidth}{8pt}
\end{center}

\begin{multicols}{2}

\textsc{\bfseries \Large Experience} \\
\\
\textsc{\large Student }
\vspace{4pt} \hrule \vspace{4pt}

{\bfseries Physics Education}, MA \hfill University of Virginia -- 2012 \\
{\bfseries Aerospace Engineering}, BS \hfill Texas A\&M University -- 2007\\

\vspace{8pt}
\textsc{\large Teacher \hfill 2008 --- }
\vspace{4pt} \hrule \vspace{4pt}
{\bfseries Fossil Ridge High School} \hfill Keller ISD -- Fort Worth, TX \\
\\
Since 2008 I have taught Geometry, Physics, Astronomy, Calculus, and Engineering. I grew the Astronomy program from less than 20 students to over 120. I doubled the enrollement in AP Calculus and produced more students with passing AP scores in school history. I am a vocal member of the district's technology committee. \\

\vspace{8pt}
\textsc{\large Entrepreneur \hfill 2013 --- }
\vspace{4pt} \hrule \vspace{4pt}
{\bfseries Hone School} \hfill Founder, Instructor, Developer\\
\\
An after school program which teaches students the fundamentals of robotics and programming. Our vision is to develop this into a pathway through which students earn marketable skills oustide existing education frameworks. My roles: teaching, writing curriculum, managing our website/curriculum webapp. 

\columnbreak


\textsc{\bfseries \Large Skills} \\
\\
\textsc{\large Proficient }
\vspace{4pt} \hrule \vspace{4pt}
{\Large \bfseries Python, Jinja2, HTML/CSS, webapp2, \LaTeX, Twitter Bootstrap} \\
\\
\textsc{\large Developing }
\vspace{4pt} \hrule \vspace{4pt}
{\Large Ruby, JavaScript, KnockoutJS, Flask, Django} \\

\vspace{10pt} 
\textsc{\bfseries \Large Other Work} 
 \vspace{10pt} 

{\bfseries EdTech DFW Meetup } \\
I founded and currently help organize this meetup for local entrepeneurs and educators in the Dallas/Fort Worth area. 
\\
\vspace{10pt}

{\bfseries University of Texas, Astronomy Department} \\
Through a teacher program sponsored by UT-Austin, I have participated in a nightime observing run on telescopes at the Mauna Kea Observatory, Hawaii; delevered workshops to teachers at the McDonald Observatory; and traveled annually to the American Astronomical Society Meetings throughout the county. 
\\


\end{multicols}

\vspace{10pt} 

\begin{center}
\rule{\textwidth}{4pt}
\end{center}

\textsc{\bfseries \Large Web Development} \\

\begin{multicols}{3}

{\bfseries lessonwell \hfill Mercurial (Kiln)} \\
\textit{www.lessonwell.com} \\
Content-management system for my calculus class. Python on Google App Engine, integrated with the Stripe API. Over 130 other teachers are using it to share their lessons with their classes

\columnbreak

{\bfseries Hone School \hfill Git (Kiln)} \\
\textit{www.honeschool.com} \\
Curriculum app for our robotics and programming afterschool program. A one page website built on KnockoutJS and derived from lessonwell. Also Python on Google App Engine. 

\columnbreak

{\bfseries Personal Website \hfill Git (Github)} \\
\textit{www.qdonnellan.com} \\
My public sandbox and professional portfolio built with  Python on Google App Engine. My blog located here represents my first attempt at a one-page webapp built on KnockoutJS

\end{multicols}

\begin{multicols}{3}

{\bfseries Calculus on Chrome } \\
\textit{calculusonchrome.appspot.com} \\
After my work on qCalculus, I desired a simple platform to put my Calculus lessons online. This webapp was my first venture into responsive web design (bootstrap). Python on Google App Engine.  

\columnbreak

{\bfseries speculess} \\
\textit{speculess.appspot.com} \\
A lens review website for users of the micro-4/3 photography platform. This app allows users to recommend lenses and suggest uses for each lens. Python app on Google App Engine. 

\columnbreak

{\bfseries qCalculus} \\
\textit{qcalculus.appspot.com} \\
After completing the Udacity CS253 Web Development class, I built this app to be the web portal for my Calculus class. UI Elements were modeled after my Udacity and Khan Academy influences. 

\end{multicols}


\end{document}
